A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-11-11 paper/paper.tex
TODO list added to paper, abstract updated. Tested everything.

\author{Dennis L. Jackson}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
\needsworklater{ We develop a classical density functional theory for
  water by combining the fundamental-measure theory functional--which
  describes hard sphere fluids--with attractive interactions.  Using
  this approximation, we are able to describe various properties of
  water near liquid-vapor and liquid-solid interfaces.  We plan to use
  this functional as the foundation for a efficient method for
  predicting the interactions of chemicals in aqueous solution on an
  atomic level.}
\end{abstract}

\maketitle

>>>>

\author{Jessica Hughes}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}
\author{Eric Krebs}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University, Corvallis, OR 97331}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
{We develop a classical density functional theory for water by combining the
fundamental-measure theory functional--which describes hard sphere fluids--with
attractive interactions based on the Statistical Associating Fluid Theory
(SAFT-VR). Using this approximation with an additional length scale parameter, we are able to describe the vapor pressure, saturated liquid density, surface tension, and enthalpy of water, as well as the number of hydrogen bonds and density oscillations formed near hydrophobic rods and spheres immersed in water. 
\needsworknow{For two rods being pulled apart, a transition occurs 
from a vapor state to a liquid state in the area between
the rods at approximately $(\pi-2)$ multipled by the radius. Even 
for nanoscale rods (radius 0.5~-~1.0~nm), we find that in the
vapor state, the force can be approximated
classically and is equal to 144~mN/m, or twice the bulk surface tension.
(Keep this? Add spheres stuff?)}
This functional is computationally efficient and provides a foundation for 
future work describing interactions in aqueous solution on an
atomic level.}
\end{abstract}
\maketitle

{\begin{itemize}
\color{blue}
\item Put finished things up here
\item[JRH] Rewrite abstract (copying from project)
\color{red}
\item[JRH] Rewrite and join introductions
\item[JRH] Work on abstract
\item[DJR] Read and edit changes to abstract
\item[DJR] Look through theory section for stuff to cut
\item[DJR,JRH] Find figures to cut
\item[JRH] Cut the test-particle section
\item[JRH] Decide what to do with slit (cut?)
\item[DJR] Write text (or clean up existing) for hard sphere solutes
\item[EJK] Add 4-rods figures
\item[EJK] Add 4-rods text
\end{itemize}
}
